%====================
% ILAB course
%====================
\subsection{{\href{https://github.com/Hollbrok/Ilab-2020-21}{Intel ILAB course}  \hfill 2020 --- 2021}}
\subtext{Key Achievement/Projects:}

\begin{zitemize}
\item Acquired the skills of working with standard I/O.
\item Gained experience in working with different data structures.
\item Learned such a primitive as CPU simulation.
\item Learned how to work with graphics by implementing a raycasting primitive.
\item Gained vast experience of working with a binary tree by implementing a differentiator and a programming language.
\end{zitemize}

\

%====================
% Lunev course
%====================
\subsection{{\href{https://github.com/Hollbrok/System-Programming}{MIPT Computer Technology course by Lunev} \hfill 2021 --- 2022}}
\subtext{Key Achievement/Projects:}

\begin{zitemize}
\item Learned a lot about the Linux PI: system programming concepts, I/O models, processes, memory, signals, threads, daemons, IPCs, sockets.
\item Learned how to write completely safe and portable code.
\item Learned the following primitives: code coverage, gcov/lcov, tests, valgrind.
\item Learned a lot about UNIX Network Programming.
\end{zitemize}

\

%====================
% Huawei HiSilicon
%====================
\subsection{{Huawei HiSilicon CPU and OS simulation course \hfill 2021 --- 2022}}
\subtext{Key Achievement/Projects:}

\begin{zitemize}
\item Got a lot of applied knowledge about how the CPU works and how to simulate it.
\item Acquired the skills to work on a project together.
\item Gained knowledge about LLVM, Cosimulation and MMU.
\item Implemented a cosimulation primitive.
\end{zitemize}

